upwell_IDX

### 2019-08-21 SST_patterns.Rmd
Calculated upwelling index quantiles

library(tidyverse)
# library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
library(heatwaveR)
library(viridis)
library(ggrepel)
library(maptools)
library(sp)
library(geosphere)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
library(ncdf4)
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
```

>>>>

library(tidyverse)
library(lubridate)
library(ggpubr)
library(zoo)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
library(heatwaveR)
library(viridis)
library(ggrepel)
library(maptools)
library(sp)
library(geosphere)
library(PBSmapping)
library(scales)
# library(grid)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
# library(ncdf4) # This was used to process NetCDF files in an earlier version
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
```

### 2019-08-21 upwell_IDX.Rmd
Calculated upwelling index quantiles

@@

wind_daily_season_test <- wind_daily_season %>% 
  group_by(season, temp_sites) %>% 
  arrange(mean_speed) %>% 
  summarize(msp_1st = quantile(mean_speed, probs=0.33, na.rm=TRUE),
            mspeed_2nd = quantile(mean_speed, probs=0.66, na.rm=TRUE))

>>>>

# Calculate quantiles of upwelling index
SACTN_upwell_quantiles <- SACTN_upwell %>% 
  group_by(site) %>% 
  summarize(quant_10 = quantile(ui.saws, probs = 0.10, na.rm = TRUE),
            quant_25 = quantile(ui.saws, probs = 0.25, na.rm = TRUE),
            quant_50 = quantile(ui.saws, probs = 0.50, na.rm = TRUE),
            quant_75 = quantile(ui.saws, probs = 0.75, na.rm = TRUE),
            quant_90 = quantile(ui.saws, probs = 0.90, na.rm = TRUE))

@@

wind_daily_season_test <- wind_daily_season %>% 
  group_by(season, temp_sites) %>% 
  arrange(mean_speed) %>% 
  # Add the following line with mutate to filter the data and add a text label to use with an ANOVA
  summarize(msp_1st = quantile(mean_speed, probs=0.33, na.rm=TRUE),
            mspeed_2nd = quantile(mean_speed, probs=0.66, na.rm=TRUE))
